Spin canonical divisors of log stacky curves

### 2015-06-22 stacky_write_up/spin_cring.tex
changed g to h

\usepackage{tikz}
\usepackage{tikz-cd}
\usetikzlibrary{matrix,arrows,decorations.pathmorphing}

@@

\newcommand \subhalf[1]{\frac{{#1} - 1}{2{#1}}}
\newcommand{\se}[1]{\section*{Problem #1}}
\newcommand \halfcan{L}
\newcommand \Supp{\text{Supp}}
\newcommand \initial{\text{in}}
\newcommand \gin{\text{gin}}

@@

First we prove a nice result about minimal generation of ideals of relations:

\begin{lem}
\label{lem:minimal_quadratic}
Suppose $k[x_1, \ldots, x_n]\hookrightarrow k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ be graded ring, not necessarily
generated in degree 1 that are equipped with monomial ordering $\prec$.
 Let $\phi: k[x_1, \ldots, x_n] \twoheadrightarrow B, \phi':k[x_1, \ldots, x_n, y_1, \ldots, y_m]\twoheadrightarrow B'$ be maps of graded
rings with kernels $I \hookrightarrow I'$ such that the following diagram commutes:
\[
	\begin{tikzcd}
	I\ar[hookrightarrow]{r}\ar[hookrightarrow]{d} & k[x_1, \ldots, x_n]\ar[twoheadrightarrow]{r} \ar[hookrightarrow]{d} & B \ar[hookrightarrow]{d}\\
	I' \ar[hookrightarrow]{r} & k[x_1, \ldots, x_n, y_1, \ldots, y_m] \ar[twoheadrightarrow]{r}& B'
	\end{tikzcd}
\]
Further suppose that $I'$ is generated over $I$ by elements $f_1,
\ldots, f_j$ as a $k$-vector space, where $in_\prec(f_i) \in \{y_ix_j, y_iy_j\}$ and no monomial of $f_i$
is of the form $y_i$.  Then, the elements $f_i$ determine minimal
generators for $I'$ over $I$.
\end{lem}

\begin{proof}
Regrade the rings $k[x_1, \ldots, x_n], k[x_1, \ldots, x_n, y_1, \ldots, y_m]$ so that all $x_i$ and $y_j$ lie in
degree 1. Then,
\[
	\phi : k[x_1, \ldots, x_n] \twoheadrightarrow B 
\]
\[
	\phi': k[x_1, \ldots, x_n, y_1, \ldots, y_m] \twoheadrightarrow B'
\]

\noindent
determines map of rings, no longer necessarily graded. 
By assumption, $I'$ is generated over $I$ as a $k$-vector space by elements $f_1, \ldots, f_n$ whose initial terms have degree 2 and are linearly independent.  By the theory of Grobner basis,
\[
	\dim_k(B'/B)_2=\dim_k(k[x_1, \ldots, x_n, y_1, \ldots, y_m]/k[x_1, \ldots, x_n])_2 - j
\]
so
\[
	\dim_k (I'/I)_2=j.
\]
This implies any set of
generators for $I$ must have at least $j$ elements. Since $f_1,
\ldots, f_j$ is such a set, it is minimal.
\end{proof}
\begin{rem}\label{rem:minimal_quadratic_trivial_case}
It will be useful to use lemma \ref{lem:minimal_quadratic} in the case $m=0$, in which case we find explicitly that $f_1, \ldots, f_r$ are $k$-minimal generators for $I'$ (over the trivial base vector space).  
\end{rem}

We will now prove a lemma that will be used to inductively deal with divisors that are sufficiently saturated, by combining and extending methods of VZB \todo{add 
reference} and O'Dorney\todo{reference}.

@@

\begin{equation}
\label{eqn:deg1_sat_ind_dim}
	h^0(X, \lfloor{dD + d\frac{\alpha}{\beta} P \rfloor}) = h^0(X,\lfloor dD
	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \forall d \in \mathbf{
	N} : d \ge \frac{\beta}{\alpha}.
\end{equation}
Let 
\[
	0<\frac{c_1}{d_1}<...<\frac{c_n}{d_n}=\frac{\alpha}{\beta}
\]
be the non-negative best lower approximation.
Then 
\begin{itemize}
\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  
degree $d_i$ and has a pole at $P$ of degree $c_i$

\item If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then

\begin{align*}
	\initial_\prec(I') &= \initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
										 &+ \langle y_i x_j: 1 \le i \le n, 1 \le j \le m \rangle \\
										 &+ \langle y_i y_j: \lfloor \frac{\alpha}{\beta} \rfloor \rangle \le i \le j \le n-1 \\
										 &+ \langle y_i y_j: 1\le i\le j\lfloor \frac{\alpha}{\beta} \rfloor\\
										 &+ \langle (y_i)^{\deg(y_{i+1}+1)}: 1\le i=\lfloor \frac{\alpha}{\beta} \rfloor
\end{align*}
In particular, if $\frac{\alpha}{\beta}\le 1$, then $I$ is minimally generated by elements with leading terms of the form $y_ix_j$ and $y_iy_j$.
\item If $\gin_\prec(I)=\initial_\prec(I)$ then $\gin_\prec(I')=\initial_\prec(I')$.
\item A Grobner basis with the initial terms $y_i x_j$, $y_iy_j$, and possibly $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor \frac{\alpha}{\beta} \rfloor}+1}$ as shown above minimally generates $I'$.
\end{itemize}
\end{lem}

@@

Let 
\[
	0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{
\beta}
\] 
be the non-negative best lower approximation of $\frac{
\alpha}{\beta}$.  Note that elements of $H^0(X,dD')$ have pole of
orders ranging from 0 to $\lfloor d_i \frac{\alpha}{\beta}\rfloor =
c_i $ at $P$.  A set of these one for each pole degree 1 to $\lfloor
d_i \frac{\alpha}{\beta} \rfloor$ are linearly independent from
each other and $(R_D)_d$, so by degree considerations, they span
$(R_{D'})_d$ over $(R_D)_d$ as $k$-vector spaces.

For any $j < i$, $\frac{c_i}{d_i} > \frac{c_j}{d_j}$
by construction, so any product of $\prod z_i$ of elements of
degrees less than $d_i$ must have 
\[
	\frac{-\ord(z_i)}{\deg(z_i)} < \frac{c_i}{d _i},
\]
so we have the pole order of $\prod z_i$ is 
\[
	\sum -\ord(z_i) = d_i(\frac{\sum -\ord( z_i)}{\sum \deg( z_i)}) < d_i\frac{c_i}{d_i} = c_i .
\] 
Thus, the elements of $(R_{D'})_{d_i}$ with pole order $c_i$ at $P$ are not generated by 
lower degrees.  
Generically choose some $y_i \in(R_{
D'})_{d_i}$ to have maximal pole order at $P$ (note that if $d_i=1$ then 
\[
	-\ord_P(y_i)= \max(c_j:d_j=1)
\]
and if more than one $d_i$ is 1, we
must also choose them generically so they generate $(R_{D'})_1$).

Suppose $d\le \beta$ and positive $\frac{c}{d} \le \frac{\alpha}{
\beta}$ not a best lower approximation.  Then choose
best lower approximation $\frac{c_i}{d_i}$ such that $c_i\le c$ is
maximal; since $c<c_{i+1}$, $\frac{c_i}{d_i}\ge \frac{c}{d}$.  From
this we can deduce that 
\[
	c_i+(d-d_i) \lfloor \frac{\alpha}{\beta} \rfloor \ge c.
\]  
Therefore, we can generate an element of $(R_{D'})_d$ as a product of lower degrees that 
has pole degree $c$ at $P$ by either $y_i u^b$ or $y_i z u^b$, or $zu^b$ satisfying $i>
\lfloor \frac{\alpha}{\beta} \rfloor$ and $z=y_j (y_{\lfloor \frac{\alpha}{\beta} \rfloor})^b$ 
where $d_j=1$ ($=d_{{\lfloor \frac{a}{b} \rfloor}}$) and $b<d_{\lfloor \frac{\alpha}{\beta} 
\rfloor + 1}$.  
Thus, for a general $d$ (not necessarily less than $\beta$), if $\frac{c}{d} \le
\frac{\alpha}{\beta}$ is not a best lower approximation than we can
construct an element in degree $d$ with pole degree $c$ by either $y
_n^a y_i u^b$, $y_n^a zy_iu^b$ or $y_n^a z u^b$ satisfying the
same conditions.  We notice that elements of this form are all
linearly independent in $R_{D'}$.  Thus, they form a $k$-basis for
$R_{D'}$ over $R_D$.  Thus $u, x_1, ..., x_m, y_1, ..., y_n$ generate
$R_{D'}$.

Choose $x_i\in \{x_1, \ldots, x_m\}$ and $y_j\in \{y_1, \ldots, y_n\}$, where $y_j$ 
corresponds to the best lower approximation $\frac{c_j}{d_j}$.  Recall from the previous 
paragraph that we can uniquely construct an element in degree $d$ with pole order $c$ at 
$P$ by elements of the $y_n^a y_l u^b$ and $y_n^a y_l y_{l'} u^b$ with $d_l=1$ and if 
$d_{l'}=1$ then $c_{l'} = \lfloor \frac{\alpha}{\beta} \rfloor$.  Specifically, we can 
successively subtract some $\gamma_l y_l u^{b_l}$, $\gamma_l y_l z_l u^{b_l}$, or $
\gamma_l z_l$ with $y_l, z_l, b_l$ satisfying the same conditions as above and $\gamma_l
\in k$ the element ensuring that the difference decreases in pole degree at $P$ by 1.  For 
convenience, we can combine these into the case $\gamma_l (y_l)^{s_l}(z_l)^{a_l}u^{b_l}$ 
with $(s_l,a_l)\in \{(1,0),(1,1),(0,1)\}$.  In the cases when $\frac{\alpha}{\beta}<1$ so $z_l$ 
is not well-defined, just pick an arbitrary element of $R_D$ for $z_l$ ensuring that the 
expression still makes sense; in such cases we will always choose $a_l=0$ so this choice 
is irrelevant, and only makes writing out cases more convenient.  Therefore, we can write
\[
	x_i y_j - \sum_{l} (y_l)^{s_l} (z_l)^{a_l} u^{b_l}\in R_D
\]
giving us a non-trivial relation with leading term $x_iy_j$. \todo{Explicitly state ordering at 
the beginning}

Similarly, suppose $y_i,y_j\in \{y_1, \ldots ,y_{n-1}\}$ with $1<d_i$ and $j\ge i$ (that is, so 
$y_iy_j$ does not appear as a basis element of the form described above: $y_n^0 y_jy_i 
u^0$).  Choose the maximal $l$ such that $c_h\le c_i+c_j$; since $1<d_i\le d_j$, $(c_i
+c_j)-c_j>\lfloor \frac{\alpha}{\beta}\rfloor$ so $c_{j+1} < c_i + c_j$ meaning $c_h \ge c_{j
+1} > c_j$.  Furthermore, $c_i + c_j - c_h<\lfloor \frac{\alpha}{\beta} \rfloor$ so either 
$c_h=c_i+c_j$ or there is some $h'$ such that $c_{h'}=c_i+c_j-c_l$ and $d_{h'}=1$.  Since 
$\frac{c_h}{d_h}$ is a best lower approximation of $\frac{\alpha}{\beta}$ with denominator 
larger than those of $\frac{c_i}{d_i}$ and $\frac{c_j}{d_j}$, we know that since $c_h\le c_i
+c_j$ we must have $d_h<d_i+d_j$.  Thus in the case with a $y_{l'}$ term we have $d_h + 
d_{h'} = d_h + 1 \le d_i + d_j$.  That is to say, by choosing $b-d_i+d_j-ad_h-1$ we find 
(where $a\in\{0,1\}$ corresponding to if a $y_{h'}$ appears) that $y_h(y_h')^au^b$ and 
$y_iy_j$ both lie in degree $d_i+d_j$ with pole order $c_i+c_j$ at $P$.  From here we can 
follow a similar technique as in the previous paragraph to cancel out poles of $y_iy_j$ at $P
$ to find
\[
	y_iy_j-\gamma_h (y_h)^{s_h}(z_{h})^{a_h}u^{b_h}-\sum_l (y_l)^{s_l} (z_{l})^{a_l}
u^{b_l}\in R_D
\]
implying a relation with initial term $y_i y_j$.

Next, suppose $y_i, y_j\in \{y_1, \ldots ,y_{n-1}\}$ such that $i\le j$, $d_j=d_i=1$, and $d_{j
+1}=1$ (i.e. $c_i, c_j \le \lfloor \frac{\alpha}{\beta} - 1 \rfloor$).  If $i>1$ and then $y_{j+1}
y_{i-1}$ lies in the same degree as $y_iy_j$ (degree 2) with the same pole order; following 
the same method as the previous two paragraphs we find
\[
	y_i y_j - \gamma y_{i-1} y_{j+1} - \sum_{l} (y_l)^{s_l} (z_l)^{a_l}u^{b_l}\in R_D.
\]
Similarly if $i=1$, then we get the same result using
\[
	y_i y_j - \gamma u y_{j+1} - \sum_l y_l u^{b_l} \in R_D.
\]
In both cases we deduce that $y_iy_j$ is an initial term of some relation.

Finally, we examine the case (for $\alpha \ge \beta$) of $(y_i)^{i + 1}$ when $i=\lfloor 
\frac{\alpha}{\beta}\rfloor$.  If $\beta=1$, then there are no relations with initial term a 
power of $y_i$ and we are immediately done.  Otherwise, assuming $\beta\ne 1$, we note 
that $c_id_{i+1}=c_{i+1}d_i+1=c_{i+1}+1$. \todo{reference to Evan's paper where he 
proves this}  Therefore, if $i>1$ then $c_i^{d_{i+1}+1}$ and $c_{i-1} c_{i+1}$ both lie in the 
$d_{i+1}+1$ degree with pole order $c_{i+1}+1$.  Following a similar technique to the 
previous paragraphs we find
\[
	(y_i)^{c_{i+1}+1} - y_{i+1} y_{i-1} - \sum_l (y_l)^{s_l}(z_l)^{a_l} u^{b_l}.
\]
Similarly if $i=1$ then
\[
	(y_i)^{c_{i+1}+1}-y_{i+1}u-\sum_l (z_l)^{a_l} u^{b_l}.
\]
In each case we demonstrate $(y_i)^{c_{i+1}+1}$ as the initial term of a relation.

Let $J'$ be the ideal of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ generated by the initial 
terms described in the previous paragraphs together with $\gin_\prec(I)k[u, x_1, \ldots, 
x_m, y_1, \ldots, y_n]$.  We show that $J$ is in fact all of the initial ideal.  Suppose $f$ is a 
non-constant monomial that does not lie within $J$.  Further suppose $f$ does not lie in 
$k[u, x_1, \ldots, x_m]$.  Then there is some $y_i|f$.  Since $f\not\in j$, we cannot have 
some $x_j|f$ or else we would have $y_ix_j|f$ contradicting $f\not\in J$.  Furthermore, if 
$y_l|f$ for $l<i$, then we must have $d_l=1$ or else $y_ly_i$ is an initial element of a 
relation and divides $f$.  If $d_i=1$ as well, then we must have $c_i=\lfloor \frac{\alpha}
{\beta}\rfloor$, or else $y_iy_l\in I$; finally we can not have $(y_{\lfloor \frac{\alpha}{\beta}
\rfloor})^{d_{\lfloor \frac{\alpha}{\beta} \rfloor+1}+1}|f$.  We observe that the remaining 
elements are precisely those of the form $y_n^a y_i u^b$, $y_n^a zy_iu^b$, and $y_n^a z 
u^b$ which are the elements of our chosen $k$-basis for $k[u, x_1, \ldots, x_m, y_1, \ldots, 
y_n]/I'$ over $k[u, x_1, \ldots, x_m]/I$.  Therefore, by dimension counting (in each degree), 
we see that $J'$ is the initial ideal of $I'$.  Furthermore, since our choice of $y_i$s was 
generic, this is in fact the generic initial ideal.

In the case when all $\frac{\alpha}{\beta}\le 1$, lemma \ref{lem:minimal_quadratic} immediately tells us that the Grobner basis defined above is minimal.
\todo{What about $\frac{\alpha}{beta}>1$?}
\end{proof}

\begin{rem}\label{rem:deg1_sat_ind_gen_rel_degrees}
Notice that in lemma \ref{lem:deg1_sat_ind}, $D'$ is generated in degree at most $\max(\delta,\beta)$ with relations generated in degree at most $\max(\tau,\delta+\beta,2\beta)$
\end{rem}

This yields some immediate corollaries:

\begin{cor}\label{cor:effective_Q_divisor_can_ring}
If the genus of $X$ is 0 and $D\sim\sum \frac{\alpha_i}{\beta_i} P_i$ is linearly equivalent to an effective $\mathbf{Q}$ divisor of $X$, then $R_D$ is generated in degree at most $\max(\beta_i,1)$ with relations generated in degree at most $2\max(\beta_i,1)$.
\end{cor}

\begin{proof}
We can prove this by induction.  As a base case, let $D\sim 0$.  Then $R_D\cong k[x]$ which is generated in degree 1 with no relations, satisfying the inductive hypothesis.
Now, suppose the result is proven for all effective $D$ with support at most $r$ points; then if $D'\sim \sum_{i=1}^{r+1} \frac{\alpha_i}{\beta_i}$, we set $D=\sum_i^{r} \frac{\alpha_i}{\beta_i}$.  By hypothesis, $R_D$ is generated in degree at most $\max_{1\le i\le r}(\beta_i)$ with relations generated in degree at most 2$\max_{1\le i\le r}(\beta_i)$.  Since $D$ is effective, the condition of equation \ref{eqn:deg1_sat_ind_dim} is met, so by remark \ref{rem:deg1_sat_ind_gen_rel_degrees} of lemma \ref{lem:deg1_sat_ind}, $R_{D'}$ is generated in degree at most $\max(\beta_i)$ with relations generated in degree at most $2\max(\beta_i)$.
\end{proof}

\begin{cor}\label{cor:genus_0_posiive_delta}
Let $\halfcan$ be a stacky log spin canonical divisor of signature $(0,e_1,...,e_n,\delta)$ with $\delta>0$.  Then 
\end{cor}
\begin{proof}
Since $\halfcan$ is a half canonical divisor, 
\[
	2\halfcan=D+\sum \subhalf{i}P_i
\] 
where 
\[
	D\sim K_X+\Delta\sim -2\infty+ \Delta
\] is a divisor of $X$ (i.e. with 
possibly negative integer coefficients).  Since $\Delta$ is non-
zero effective, $\deg(D)\ge -1$.   Noting that the coefficient of 
any point $P$ occurring in a stacky divisor of $\sx$ must have 
coefficient lying in $\mathbf{Z}[\frac{1}{e_i}]$ (ranging over $e_i$
s appearing in the characteristic of $(\sx,\Delta)$).

Since all $e_i$s are odd, $2$ cannot appear in a denominator of the 
coefficient of a point $P$ in $\halfcan$, meaning that $\frac{D}{2}$
 must be a $X$-divisor.  Since $\deg(\frac{D}{2})=\frac{1}{2}\deg(D)
\ge -\frac{1}{2}$, we in fact have $\deg(D)\ge 0$.  Thus $\halfcan$ 
is linearly equivalent to an effective $X$ divisor plus $\sum 
\subhalf{i}P_i$.  We have thus shown $\halfcan$ is linearly equivalent to an effective divisor.  Thus, by \ref{cor:effective_Q_divisor_can_ring} the desired result follows.
\end{proof}

\begin{cor}
Let $D$ be a fractional $\frac{a}{b}$-canonical divisor of a genus 0 stacky curve with denominator $b > 2$ when $\frac{a}{b}$ is written in reduced form.
\end{cor}
\begin{proof}
For a similar reason as in corollary \ref{cor:genus_0_posiive_delta}, $D$ must be equivalent to an effective divisor (in this case even when $\delta=0$), so by corollary \ref{cor:effective_Q_divisor_can_ring} we get the desired result.
\end{proof}

\todo{Add higher genus corollaries once we figure out what we want to say there}

@@

	\hline
	\hline

@@

\begin{prop}
\label{prop:sat_three_induction}
\todo{Make explicit assumptions on genus.}
\todo{Should switch either $R$ and $R'$ or $\sx$ and $\sx'$ to make prime notation consistent (note that inclusion is reversed since this map adds a stacky point to $\sx$; note that we should also say that this map is only ramified at $P$), Aaron: you're right, I wrote the inclusion on rings in the wrong direction. Actually, the map isn't ramified at $P$, it's just defined away from $P$. I decided to remove this from the proposition though.} Let $R_{L'} = R' = k[x]/I'= k[x_3, x_4
, x_5,\ldots, x_m]/I'$ satisfy $sat(Eff(D')) = 3.$ Let $L = L' + \frac{1}{
3}P$, and let $R = R_L$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that the ordering on $k[x]$ satisfies 
\begin{align*}
	\ord_{x_3}(f) < \ord_{x_3}(g) \implies f \prec g.
\end{align*}
Then, the following statements hold.

@@

\begin{enumerate}
	\item[(Ad-i)] Suppose for all $i \in J$, there exists $y_{i,e_i'} 
		\in R'$ so that $R'$ admits a presentation
		\begin{align*}
			R' \cong \left( k[x] \otimes k[y_{i,e_i'}]_{i \in J} \right)/I'
		\end{align*}
		so that for all $i \in J$ we have $\deg y_{e_i'} = e_i'$ and $-ord_{
		Q_i}(y_{i,e_i'}) = \frac{e_i'-1}{2}$.
	\item[(Ad-ii)] For all $i \in J$, any generator $z \neq y_{i,e_i'}$
		of $R'$ satisfies
		\begin{align*}
			\frac{- ord_{Q_i}(z)}{\deg z} < \subhalf {e_i'}.
		\end{align*}
	\item[(Ad-iii)] For all $i \in J$ we have
		\begin{align*}
			\deg \lfloor e_i L \rfloor \geq 2g - 1 + \max_{d \geq 0} \# S_{\sigma, J}(i, d)
		\end{align*}
		\todo{Check the 2g - 1, in particular, David seems to think we are usually 1 off and possibly 2 off when g = 1. I have a feeling this is a mistake, but don't understand why.} 
		where
		\begin{align*}
			S_{\sigma, J}(i, d) := \{j \in J : j \neq i \text{ and } e_j'+2d
			\mid e_i - e_j'\}
		\end{align*}
\end{enumerate}
\end{defn}

@@

\begin{enumerate}
	\item[(a)] $\sigma_1 = (0; 3, 3, 11; 0), J_1 = \{3\}$
	\item[(b)] $\sigma_2 = (0; 3, 5, 9; 0), J_2 = \{2, 3\}$
	\item[(c)] $\sigma_3 = (0; 5, 5, 7; 0), J_3 = \{1, 2, 3\}$
	\item[(d)] $\sigma_4 = (0; 3, 3, 3, 5; 0), J_4 = \{1, 2, 3, 4\}$
	\item[(e)] $\sigma_5 = (0; 3, 3, 3, 3, 3; 0), J_5 = \{1, 2, 3, 4, 5\}$
\end{enumerate}
\end{lem}

@@

\begin{enumerate}
	\item[(a)] $(\deg \lfloor e_3 L \rfloor, \max_{d \geq 0} \# S_{(
		\sigma_1, J_1)}(3)) = (1, 0)$

>>>>

\usepackage{tikz}
\usetikzlibrary{matrix,arrows,decorations.pathmorphing}

@@

\newcommand \subhalf[1]{\frac{{#1} - 1}{2{#1}}}
\newcommand{\se}[1]{\section*{Problem #1}}
\newcommand \halfcan{L}
\newcommand \Supp{\text{Supp}}
\newcommand \initial{\text{in}}

@@

Then we find $2\halfcan=D+\sum \subhalf{i}P_i$ where $D\sim K_X+
\Delta\sim -2\infty+ \Delta$ is a divisor of $X$ (i.e. with 
possibly negative integer coefficients).  Since $\Delta$ is non-
zero effective, $\deg(D)\ge -1$.   Noting that the coefficient of 
any point $P$ occurring in a stacky divisor of $\sx$ must have 
coefficient lying in $\mathbf{Z}[\frac{1}{e_i}]$ (ranging over $e_i$
s appearing in the characteristic of $(\sx,\Delta)$).

Since all $e_i$s are odd, $2$ cannot appear in a denominator of the 
coefficient of a point $P$ in $\halfcan$, meaning that $\frac{D}{2}$
 must be a $X$-divisor.  Since $\deg(\frac{D}{2})=\frac{1}{2}\deg(D)
\ge -\frac{1}{2}$, we in fact have $\deg(D)\ge 0$.  Thus $\halfcan$ 
is linearly equivalent to an effective $X$ divisor plus $\sum 
\subhalf{i}P_i$.  We have now reduced to the case of $\halfcan$ 
linearly equivalent to an effective divisor.  The result in this 
specific case in fact generalizes to any $\mathbf{Q}$-divisor: $D=\sum
\frac{\alpha_i}{\beta_i} P_i$ for $\alpha_i,\beta_i\in \mathbf{N}$.

We will prove this by induction using methods analogous to ones of VZB\todo{add 
reference}.  O'Dorney \todo{Insert reference to Theorem 4} provides a base case when $D
\sim \frac{\alpha}{\beta} P$:
\begin{lem}\label{lem:O'Dorney_1_point}
Let 
\[
	0<\frac{c_1}{d_1}<\frac{c_2}{d_2}<...<\frac{c_r}{d_r}=\frac{\alpha}{\beta}
\] 
be the nonnegative best lower approximation\todo{define this above} of $\frac{\alpha}{\beta}
$.  Then $R_D$ is generated up to degree $\beta$ by generators $y_1,...,y_r$ where $y_i$ 
lies in degree $d_i$ with pole of degree $c_i$ at $P$.  
\end{lem}
\begin{proof}
See O'Dorney \todo{provide reference}.
\end{proof}

The following lemma extends this as well as a lemma of VZB \todo{reference to lemma 
8.3.1 in VZB} and provides a method to induct from this as well as many other base cases.

@@

\begin{equation}
\label{eqn:deg1_sat_ind_dim}
	h^0(X, \lfloor{dD + d\frac{\alpha}{\beta} P \rfloor}) = h^0(X,\lfloor dD
	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \forall d \in \mathbf{
	N} : d \ge \frac{\beta}{\alpha}.
\end{equation}
Let 
\[
	0<\frac{c_1}{d_1}<...<\frac{c_n}{d_n}=\frac{\alpha}{\beta}
\]
be the non-negative best lower approximation.
Then 
\begin{itemize}
\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  
degree $d_i$ and has a pole at $P$ of degree $c_i$
\item If $I$ and $I'$ are the ideal of relations of $R_D$ and $R_{D'}$ respectively, then

\begin{align*}
	\initial_\prec(I') &= \initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
										 &+ \langle y_i x_j: 1 \le i \le n, 1 \le j \le m \rangle \\
										 &+ \langle y_i y_j: 1 \le i \le j \le n-1 \rangle.
\end{align*}

\todo{See if we can additionally get the other information discussed in VZB theorem 8.3.1}
\end{itemize}
\end{lem}

@@

Let $0 < \frac{c_1}{d_1} < \ldots < \frac{c_n}{d_n} = \frac{\alpha}{
\beta}$ be the non-negative best lower approximation of $\frac{
\alpha}{\beta}$.  Note that elements of $H^0(X,dD')$ have pole of
orders ranging from 0 to $\lfloor d_i \frac{\alpha}{\beta}\rfloor =
c_i $ at $P$. A set of these one for each pole degree 1 to $\lfloor
d_i \frac{\alpha}{\beta} \rfloor$ are linearly independent from
each other and $(R_D)_d$, so by degree considerations, they span
$(R_{D'})_d$ over $(R_D)_d$ as $k$-vector spaces.

For any $j < i$, $\frac{c_i}{d_i} > \frac{c_j}{d_j}$
by construction, so any product of $\prod z_i$ of elements of
degrees less than $d_i$ must have $\frac{-\ord(z_i)}{\deg(z_i)} <
\frac{c_i}{d _i}$, so we have the pole order of this product is $
\sum -\ord(z_i) = d_i(\frac{\sum -\ord( z_i)}{\sum \deg( z_i)}) < d_
i\frac{c_i}{d_i} = c_i $. Thus, the elements of $R_{d_i}$

For any $j<i$, $\frac{c_i}{d_i}>\frac{c_j}{d_j}$ by construction,
so any product of $\prod z_i$ of elements of degrees less than $d_i$
 must have $\frac{-\ord(z_i)}{\deg(z_i)}<\frac{c_i}{d_i} $, so we
have the pole order of this product is $\sum -\ord(z_i)=d_i(\frac{
\sum -\ord( z_i)} {\sum \deg( z_i)})<d_i\frac{c_i}{d_i}=c_i$.
Thus, elements of $(R_{D'})d_i$ with pole order $c_i$ at $P$ are
not generated by lower degrees; generically choose some $y_i \in(R_{
D'})_{d_i}$ to have maximal pole order (note that if $d_i=1$ then $-
\ord_P(y_i)= \max(c_j:d_j=1)$ and if more than one $d_i$ is 1, we
must also choose them generically so they generate $(R_{D'})_1$).

Suppose $d\le \beta$ and $\frac{\bar{c}}{\bar{d}}\le \frac{\alpha}{
\beta}$ with $c>0$ is not a best lower approximation.  Then choose
best lower approximation $\frac{c_i}{d_i}$ such that $c_i\le c$ is
maximal; since $c<c_{i+1}$, $\frac{c_i}{d_i}\ge \frac{c}{d}$.  From
this we can deduce that $c_i+(d-d_i)\lfloor \frac{\alpha}{\beta}
\rfloor\ge c$.  Therefore, we can produce an element in $(R_{D'})_d$
 with pole degree $c$ at $P$ by either $y_i u^b$ or $y_j y_i u^b$
where $d_j=1$ and if $d_i=1$ as well then $c_i=1$. Thus, for a
general $d$ (not necessarily less than $\beta$), if $\frac{c}{d} \le
\frac{\alpha}{\beta}$ is not a best lower approximation than we can
construct an element in degree $d$ with pole degree $c$ by either $y
_n^a y_i u^b$ or $y_n^a y_j y_iu^b$ with the latter satisfying the
same conditions.  We notice that elements of this form are all
linearly independent in $R_{D'}$.  Thus, they form a $k$-basis for
$R_{D'}$ over $R_D$.  Thus $u,x_1,...,x_m,y_1,...,y_n$ generate
$R_{D'}$.

\todo{finish proof of relations, which follows easily using VZB's
method; peter will do this tomorrow (sunday)}

\end{proof}

\todo{lots of corollaries; peter can do this tomorrow}

@@

	\hline

@@

\begin{lem}
\label{lem:minimal_quadratic}
Suppose $k[x_1,\ldots, x_n]$ is a graded ring, not necessarily
generated in degree 1, is equipped with a monomial ordering $\prec$.
 Let $\phi:k[x_1,\ldots, x_n] \rightarrow B$ be a map of graded
rings with kernel $I,$ such that $I$ is generated by elements $f_1,
\ldots, f_j$, where $in_\prec(f_i) = x_ix_j,$ and no term of $f_i$
is of the form $x_k$. Then, the elements $f_i$ determine minimal
generators for $I$.
\end{lem}

\begin{proof}
Regrade the ring $k[x_1, \ldots, x_n]$ so that all $x_i$ lie in
degree 1. Then,
\[
	\phi : k[x_1, \ldots, x_n] \rightarrow B
\]

\noindent
determines a map of rings, no longer necessarily graded. Consider
the grlex monomial ordering $<$ on $k[x_1, \ldots, x_n]$.
\todo{This ordering isn't quite right. 
We need to preserve the ordering on quadratic terms}
By
assumption, the kernel $I$ is generated by elements whose initial
terms have degree 2 and are all distinct. Therefore, $\dim_k (k[x_1,
\ldots, x_n])_2 = \binom{n}{2}-j.$ This implies any set of
generators for $I$ must have at least $j$ elements. Since $f_1,
\ldots, f_j$ is such a set, it is minimal.
\end{proof}

\begin{prop}
\label{prop:sat_three_induction}
\todo{Make explicit assumptions on genus.}
\todo{Should switch either $R$ and $R'$ or $\sx$ and $\sx'$ to make prime notation consistent (note that inclusion is reversed since this map adds a stacky point to $\sx$; note that we should also say that this map is only ramified at $P$), Aaron: you're right, I wrote the inclusion on rings in the wrong direction. Actually, the map isn't ramified at $P$, it's just defined away from $P$. I decided to remove this from the proposition though.} Let $R_{L'} = R' = k[x]/I'= k[x_3, x_4
, x_5,\ldots, x_m]/I'$ satisfy $sat(Eff(D')) = 3.$ Let $L = L' + \frac{1}{
3}P$, and let $R = R_L$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that the ordering on $k[x]$ satisfies
\begin{align*}
	\ord_{x_3}(f) < \ord_{x_3}(h) \implies f \prec h.
\end{align*}
Then, the following statements hold.

@@

\begin{enumerate}
	\item[(Ad-i)] Suppose for all $i \in J$, there exists $y_{i,e_i'} 
		\in R'$ so that $R'$ admits a presentation
		\begin{align*}
			R' \cong \left( k[x] \otimes k[y_{i,e_i'}]_{i \in J} \right)/I'
		\end{align*}
		so that for all $i \in J$ we have $\deg y_{e_i'} = e_i'$ and $-ord_{
		Q_i}(y_{i,e_i'}) = \frac{e_i'-1}{2}$.
	\item[(Ad-ii)] For all $i \in J$, any generator $z \neq y_{i,e_i'}$
		of $R'$ satisfies
		\begin{align*}
			\frac{- ord_{Q_i}(z)}{\deg z} < \subhalf {e_i'}.
		\end{align*}
	\item[(Ad-iii)] For all $i \in J$ we have
		\begin{align*}
			\deg \lfloor e_i L \rfloor \geq 2g - 1 + \max_{d \geq 0} \# S_{\sigma, J}(i, d)
		\end{align*}
		\todo{Check the 2g - 1, in particular, David seems to think we are usually 1 off and possibly 2 off when g = 1. I have a feeling this is a mistake, but don't understand why.} 
		where
		\begin{align*}
			S_{\sigma, J}(i, d) := \{j \in J : j \neq i \text{ and } e_j'+2d
			\mid e_i + 2d\}
		\end{align*}
\end{enumerate}
\end{defn}

@@

\begin{enumerate}
	\item[(a)] $\sigma = (0; 3, 3, 11; 0), J = \{3\}$
	\item[(b)] $\sigma = (0; 3, 5, 9; 0), J = \{2, 3\}$
	\item[(c)] $\sigma = (0; 5, 5, 7; 0), J = \{1, 2, 3\}$
	\item[(d)] $\sigma = (0; 3, 3, 3, 5; 0), J = \{1, 2, 3, 4\}$
	\item[(e)] $\sigma = (0; 3, 3, 3, 3, 3; 0), J = \{1, 2, 3, 4, 5\}$
\end{enumerate}
\end{lem}

@@

\begin{enumerate}
	\item[(a)] $(\deg \lfloor e_3 \rfloor, \# S_{(\sigma, J)}(3)) = (1, 0)$

	\item[(b)] $(\deg \lfloor e_2 \rfloor, \#S_{(\sigma, J)}(2)) = (1, 0)$ \\
		$(\deg \lfloor e_3 \rfloor, \#S_{(\sigma, J)}(3)) = (1, 0)$
